Exploring Disparate Data: Part 1

### 2024-11-15 A3-Pt1.Rmd
update

-   Andy (169081356)
-   Dibu (169708451)
-   Oscar (169057882)
-   Taras (169099616)

@@

```{r aware_fixed_country_match}
aware_fixed_country_match <- aware_fixed_country |>
    mutate(
      # Change country using a case_when statement
      country = case_when(
        country == "Bolivia (Plurinational State of)" ~ "Bolivia",
        country == "Congo (Democratic Republic of the)" ~ "Congo, Rep.",
        country == "Egypt" ~ "Egypt, Arab Rep.",
        country == "Hong Kong" ~ "Hong Kong SAR, China",
        country == "Lao People's Democratic Republic" ~ "Lao PDR",
        country == "Slovakia" ~ "Slovak Republic",
        country == "North MAcedonia" ~ "North Macedonia",
        country == "South Korea" ~ "Korea, Rep.",
        country == "Turkey" ~ "Turkiye",
        country == "Vietnam" ~ "Viet Nam",
        country == "Yemen" ~ "Yemen, Rep.",
        TRUE ~ country
      )
    )

>>>>

-   Andy (169081356)
-   Aditya (169027493)
-   Dibu (169708451)
-   Oscar (169057882)
-   Taras (169099616)

@@

```{r aware_fixed_country_match}
aware_fixed_country_match <- aware_fixed_country |>
    mutate(
      # Change country using a case_when statement
      country = case_when(
        country == "Bolivia (Plurinational State of)" ~ "Bolivia",
        country == "Congo (Democratic Republic of the)" ~ "Congo, Dem. Rep.",
        country == "Egypt" ~ "Egypt, Arab Rep.",
        country == "Hong Kong" ~ "Hong Kong SAR, China",
        country == "Lao People's Democratic Republic" ~ "Lao PDR",
        country == "Slovakia" ~ "Slovak Republic",
        country == "North MAcedonia" ~ "North Macedonia",
        country == "South Korea" ~ "Korea, Rep.",
        country == "Turkey" ~ "Turkiye",
        country == "Vietnam" ~ "Viet Nam",
        country == "Yemen" ~ "Yemen, Rep.",
        TRUE ~ country
      )
  )
